# Resources

## Course Textbook

```{r, results='asis', echo = FALSE}
bib["finney"]
```

For homework assignments, we will refer to this book as **Textbook**.

## Graphing Calculator

Required: Choose one of the Texas Instruments TI-83/84 series (including TI-83 Plus, TI-84 Plus, TI-84 Silver Edition, TI-84 Plus CE)

I will be using **TI-84 Plus** for in-class demonstrations, but any one of the TI-83/84 models should be similar enough to follow along in class. Check this [link](https://brownmath.com/ti83/diff8384.htm#PlusSilver) to see the differences among the TI-83/84 models.

## Khan Academy{#khan}

[Khan Academy Website](https://www.khanacademy.org/)

Mr. Li's Class Code for AP Calculus AB: PHHGRQCY

Instructions:

1. [Create a Khan Academy account](https://www.khanacademy.org/signup) with your school-issued e-mail address.

2. Visit https://www.khanacademy.org/join and enter class code (PHHGRQCY). Alternatively, visit this link (https://www.khanacademy.org/join/PHHGRQCY) to join the class. Please do not join this Khan Academy classroom unless you are enrolled in Mr. Li's Calculus AB class. 

In traditional classroom formats, teachers lecture on concepts with basic examples and often do not have time to cover difficult problems. We will be using Khan Academy to flip our classroom. That is, most of your homework will involve progressing through Khan Academy modules and practice problems. In class, I will clarify concepts and delve into more challenging problems. Since I will be able to understand each student's individual progress in real time, I will adjust the format of the following day's lesson accordingly. If students are struggling in a unit, we will temporarily revert to the traditional format and review key concepts in class. In cases where students are all on track, we will have more time to engage in harder and nuanced problems as a class and in group work. In other units in which students' progress varies widely, I may use class time for individualized instruction. Based on your feedback and depending on the unit, we will make adjustments along the way. 

## Recommended Reference

```{r results='asis', echo = FALSE}
bib["barrons"]
```

If you would like more practice and preparation for the AP exam, the text above is an excellent reference. However, you are not required to purchase this text.

## Other Resource Links

[College Board: AP Calculus AB](https://apcentral.collegeboard.org/courses/ap-calculus-ab/course)

  * [Past Free Response Questions](https://apcentral.collegeboard.org/courses/ap-calculus-ab/exam/past-exam-questions)
  * AP Question Bank (will be released by College Board on August 1)

[Paul's Online Math Notes (Calculus I)](http://tutorial.math.lamar.edu/Classes/CalcI/CalcI.aspx)

# AP Exam

[2020 AP Exam Schedule](https://apcentral.collegeboard.org/courses/exam-dates-and-fees/exam-dates-2020)

  * AP Calculus AB/BC: May 5, 2020 (8 a.m. local time) 

[Exam Format](https://apcentral.collegeboard.org/courses/ap-calculus-ab/exam)

  * Section 1 (50%): 45 multiple-choice questions (1 hour, 45 min.)
      - Non-Calculator Portion: 30 questions (1 hour)
      - Calculator Portion: 15 questions (45 min.)
  * Section 2 (50%): 6 free-response questions
      - Calculator Portion: 2 questions (30 min.)
      - Non-Calculator Portion: 4 questions (60 min.)

# Grades

Final grades for each semester will be calculated as follows:

* 20% Midterm
* 20% Final Exam
* 20% Homework
* 10% Participation
* 10% Free-Response Questions
* 10% First Monthly Exam
* 10% Second Monthly Exam

## Course Exams

Each semester, the math department will administer two monthly exams, a midterm, and a final exam. Once the exam dates are finalized, they will be listed in this section.

## Homework

Homework assignments will be listed in the [Schedule](#sch) section under the date that they are assigned. Unless otherwise stated, assignments are due the following school day.

Since I can track your progress on Khan Academy, I will not ask you to turn in assignments from Khan Academy. However, I highly recommend that you work on Khan Academy questions on paper and keep your work organized for exam review.

For textbook questions, I expect the following:

1. Write your name, date, and period on the top-right corner of the first page. For subsequent pages, place just your name (without date/period) on the top-right corner.

2. On the first page, write down the assignment as the title. Example: Section 1.1 (pages 10-11, #1-36 odd) 

3. For short questions, copy down the entire problem. For longer questions, outline the problem with enough information so that you can understand the question without referring back to the textbook. The point of copying down short problems and outlining longer problems is to allow you to reference your homework problems easily for review and exam preparation.

You will receive full credit for homework as long as you write your own homework solutions and make complete corrections with a pen when we go over solutions in class.

## Participation

During class, you will have the opportunity to solve problems on the board. This is not only good practice for verbal communication of mathematics but also a great way to solidify your understanding of concepts. After each time at the board, you will sign your name on a sheet so I can tally your participation frequency. As long as you maintain regular participation, you will receive full points in this area.

## Free Response Questions

In class, we will work on previous free response questions that relate to the concepts that we cover in each unit. To simulate the scoring process, I will ask students to exchange free response papers to grade as I go through the solutions and assignment of points. After you receive your scored free response paper, you should use a pen with a different color to correct your mistakes to receive full credit.

# Policies

## Integrity

Honesty is the best policy. We will conduct this course on an honor system. This means that we will trust each other to maintain integrity. Please do not cheat or aid others in cheating.

## Collaboration Policy

While I highly encourage students to help each other in this course, please observe the following guidelines:

  * First try to work on problems on your own. Give yourself time to think through problems.
  * If you require additional help, please feel free to work collaboratively with other students on a separate piece of paper. In the process of helping each other, please do not rush through the steps to reach a solution. Allow students struggling with the problem more time to think through each step with minor hints so that they can arrive at the final solution on their own.
  * At the end of collaboration, you should still write your own homework solutions from start to finish. Do not short-change your own learning process by copying answers.


<!-- Worksheet 1 -->

<!-- \begin{multicols}{2} -->

<!-- 1. $$\int_2^3 x^2 dx$$ -->

<!--     a. 3 -->
<!--     b. $x^2$ -->
<!--     c. 6 -->
<!--     d. 7 -->

<!-- 2. $\frac{2}{3}$ -->

<!-- 3. $\sum_{n=1}^{\infty} 2^{-n} = 1$ -->

<!-- 4. $\prod_{i=a}^{b} f(i)$ -->

<!-- 5. $\int_2^3 x^2 dx$ -->

<!-- 6. $\frac{2}{3}$ -->

<!-- 7. $\sum_{n=1}^{\infty} 2^{-n} = 1$ -->

<!-- 8. $\prod_{i=a}^{b} f(i)$  -->

<!-- <!-- \end{multicols} -->

<!-- Testing one column  -->

<!-- \begin{multicols}{2} -->

<!-- 1. $$\int_2^3 x^2 dx$$ -->

<!--     a. 3 -->
<!--     b. $x^2$   -->
<!--     c. 6   -->
<!--     d. 7 -->

<!-- 2. $\frac{2}{3} $ -->

<!-- 3. $\sum_{n=1}^{\infty} 2^{-n} = 1$ -->

<!-- \vfill\null -->
<!-- \columnbreak -->

<!-- 4. $\prod_{i=a}^{b} f(i)$ -->

<!-- 5. $\int_2^3 x^2 dx$ -->

<!-- 6. $\frac{2}{3} $ -->

<!-- 7. $\sum_{n=1}^{\infty} 2^{-n} = 1$ -->

<!-- 8. $\prod_{i=a}^{b} f(i)$  -->

<!-- \end{multicols} -->

# Curricular Requirements

[College Board AP Calculus AB and BC Course and Exam Description](https://apcentral.collegeboard.org/pdf/ap-calculus-ab-bc-course-and-exam-description-0.pdf?course=ap-calculus-ab)

Page 17: Exam weighting of each unit for multiple-choice exam
Pages 20--23: Topics for each unit
  
  * In the [Schedule](#sch) section, I will use block quotes to denote the topic we are covering along with the course objectives, which the College Board broadly classifies into `CHA` (Change), `LIM` (Limits), and `FUN` (Analysis of Functions).
  
<!-- Testing testing. \index{CR5} -->
