--- 
title: "AP^&reg;^ Calculus AB & BC Syllabus"
author: ""
date: "2019--2020"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    toc_depth: 2
    config:
      sharing: null
        # facebook: false
        # twitter: false
documentclass: article
fontsize: 12pt
#toc: no
bibliography: [book.bib, packages.bib]
csl: apa.csl
link-citations: yes
github-repo: ap-calculus/ab-syllabus
description: "This notebook includes a syllabus and detailed course schedule for AP Calculus AB and BC."
always_allow_html: yes
classoption: fleqn
subparagraph: yes
# classoption: twocolumn
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='png')
mon <- as.Date("2016-08-15")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("book.bib")
BibOptions(bib.style = "authoryear", style="markdown", first.inits=FALSE, max.names = 4, check.entries = FALSE)

#https://stackoverflow.com/questions/46260431/include-the-text-of-a-bibentry-in-the-rmarkdown-text-body-output
library(bibtex)
biblio <- bibtex::read.bib(file="book.bib")
```
# Course Description

**Prerequisite:** IGCSE Additional Mathematics or Trigonometry/Pre-Calculus

AP^&reg;^ Calculus AB is a one-year course that covers the first semester of college calculus. We will cover all topics covered in the AP Calculus AB exam, including limits, continuity, differentiation, integration, and major theorems and applications of calculus.

AP^&reg;^ Calculus BC covers the first two semesters of college calculus. We will cover all AB topics at an accelerated pace as well as BC-only topics, including parametric equations, polar coordinates, and infinite series.

# Contact Information

**Teacher**: Mr. Li

**Course Website**: [https://ap-calculus.github.io](https://ap-calculus.github.io){target="_blank"}

**Office Hours**: [https://ap-calculus.github.io/#officehours](https://ap-calculus.github.io/#officehours){target="_blank"}

  * You are welcome to stop by anytime during scheduled office hours without an appointment.
  * If I need to reschedule office hours, I will send an e-mail to the class.
  * If you cannot make it to my office hours, please [schedule an appointment](https://ap-calculus.github.io/#officehours){target="_blank"}. If none of the time slots work for you, check with me after class so we can arrange a time to meet.
  
# Course Objectives

1. Develop mastery in univariate calculus concepts.
2. Apply differentiation and integration to solve real-world problems.
3. Build connections between mathematical proofs and intuition.
4. Communicate mathematical ideas clearly in both written and oral form.
5. Exercise resilience in independent problem solving.
6. Collaborate with classmates in problems involving teamwork.


