--- 
title: "AP^&reg;^ Calculus AB Syllabus"
author: "Mr. Li"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: article
fontsize: 12pt
#toc: no
bibliography: [book.bib, packages.bib]
csl: apa.csl
link-citations: yes
github-repo: ap-calculus/ab-syllabus
description: "This notebook includes a syllabus and detailed course schedule for AP Calculus AB."
always_allow_html: yes
classoption: fleqn
subparagraph: yes
# classoption: twocolumn
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='png')
mon <- as.Date("2016-08-15")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("book.bib")
BibOptions(bib.style = "authoryear", style="markdown", first.inits=FALSE, max.names = 4, check.entries = FALSE)

#https://stackoverflow.com/questions/46260431/include-the-text-of-a-bibentry-in-the-rmarkdown-text-body-output
library(bibtex)
biblio <- bibtex::read.bib(file="book.bib")
```
# Course 

## Contact

**Teacher**: Mr. Li

**E-mail**:

**Course Website**: https://scholar.netlify.com/calc-ab

**Office Hours**: TBD

  * You are welcome to stop by anytime during scheduled office hours without an appointment.
  * If I need to reschedule office hours, I will send an e-mail to the class.
  * If you cannot make it to my office hours, please [schedule an appointment](https://scholar.netlify.com/#contact). If none of the time slots work for you, check with me after class so we can arrange a time to meet.



## Course Description

**Prerequisite:** IGCSE Additional Mathematics or the equivalent of Trigonometry/Pre-Calculus

AP^&reg;^ Calculus AB^[AP is a registered trademark of the College Board, which does not endorse and was not involved in the production of this document or any part of this website.] is a one-year course that covers the first semester of college calculus. We will cover all topics covered in the AP Calculus AB exam, including limits, continuity, differentiation, integration, and major theorems and applications of calculus.

## Course Objectives

1. Develop mastery in univariate calculus concepts.
2. Apply differentiation and integration to solve real-world problems.
3. Build connections between mathematical proofs and intuition.
4. Communicate mathematical ideas clearly in both written and oral form.
5. Exercise resilience in independent problem solving.
6. Collaborate with classmates in problems involving teamwork.


